---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Manuel Melendez"
output:
  html_document:
    theme: cerulean
    highlight: kate
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE,fig.width=6,fig.height=4)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
raw_df <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/ncaa-womens-basketball-tournament/ncaa-womens-basketball-tournament-history.csv")

dplyr::glimpse(raw_df)

```

<br><br>

## Question 1

#### Do 5th seeded players have more losses than 3rd seeded players during the regular season? 

### Methods
```{r Question 1}
raw_df%>%#use this data set
  rename(reg_loss=`Reg. L`)%>%#rename column so its easier to work with
  filter(Seed%in% c("3","5"))%>%#only show 3rd and 5th seed
  ggplot()+#create ggplot with new data set made above
  aes(x=Seed,
      y=reg_loss,
      fill=Seed)+#define x/y axis
  geom_col()+#create bar plot
  labs(y="Regular Season Loses")+#change y axis name
  theme(legend.position = "none")#remove legend, not needed
  
```

### Answer

The answer is yes. 5th seeded teams have more losses than 3rd seeded teams. The graph shows 5th seeded teams have about 1,000 loses, while the 3rd season teams have about 850 loses. 


<br><br>

## Question 2

#### Do first seeded teams have a higher average of tournament wins compared to second seeded teams? 

### Methods
```{r Question 2}
raw_df%>%#use this data set
  rename(tourn_win=`Tourney W`)%>%#change column name to make easier to work with
filter(Seed%in% c("1","2"))%>%#only show 1st and 3rd seed
  ggplot()+#create ggplot using data above
  aes(x=Seed,
      y=tourn_win,
      fill=Seed)+#define x/y axis
  geom_boxplot()+#create boxplot
  labs(y="Tournament Games Won")+#rename y axis
  theme(legend.position = "none")#remove legend, not needed


```

### Answer

The answer is yes, first seeded teams have a higher average of tournament games won when compared to second seeded teams. This result is as expected since one would expect a first seeded team to be better than a second seeded team on average. The average wins for first seeded teams is about 2.5, where the average for second seeded teams is about 2 tournament wins.

<br><br>

## Question 3

#### Does stanford have more regular season wins than UCLA from 1982-2018? 

### Methods
```{r Question 3}
raw_df%>%#use this data set
  rename(reg_win=`Reg. W`)%>%#change name to make it easier to work with
  filter(School %in% c("Stanford","UCLA"))%>%#only show stanford and UCLA colleges
  ggplot()+#create ggplot using new data set created above
   aes(x=School,
       y=reg_win,
       fill=School)+#define x/y variables and add fill
  geom_col()+#create bar graph
  labs(y="Regular Season Wins")+#rename y axis
  theme(legend.position = "none")#remove legend, not needed
```

### Answer

The answer to this question is yes, Stanford has more regular season wins from 1982-2018 when compared to UCLA. Stanford has about 850 wins and UCLA only has about 325 wins. Go Stanford! 


<br><br>

## Question 4

#### Does an at home first game equate to a higher amount of tournament games won overall? 

### Methods
```{r Question 4}


```

### Answer

Replace this text with your answer to your question.
