---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Your name goes here"
output:
  html_document:
    theme: cerulean
    highlight: kate
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE,fig.width=6,fig.height=4)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
raw_df <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/ncaa-womens-basketball-tournament/ncaa-womens-basketball-tournament-history.csv")

dplyr::glimpse(raw_df)
```

<br><br>

## Question 1

#### Do 5th seeded players have more losses than 3rd seeded players during the regular season? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}
raw_df%>%#use this data set
  rename(reg_loss=`Reg. L`)%>%#rename column so its easier to work with
  filter(Seed%in% c("3","5"))%>%#only show 3rd and 5th seed
  ggplot()+#create ggplot with new data set made above
  aes(x=Seed,
      y=reg_loss,
      fill=Seed)+#define x/y axis
  geom_col()+#create bar plot
  labs(y="Regular Season Loses")+#change y axis name
  theme(legend.position = "none")#remove legend, not needed
  
```

### Answer

The answer is yes. 5th seeded teams have more losses than 3rd seeded teams. The graph shows 5th seeded teams have about 1,000 loses, while the 3rd season teams have about 850 loses. 


<br><br>

## Question 2

#### Do 1st seeded teams have a higher average of tournament wins than 3rd seeded teams? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### Does stanford have more regular season wins than UCLA from 1982-2018? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### Does an at home first game equate to a higher amount of tournament games won overall? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.
