---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Your name goes here"
output:
  html_document:
    theme: cerulean
    highlight: kate
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE,fig.width=6,fig.height=4)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
raw_df <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/ncaa-womens-basketball-tournament/ncaa-womens-basketball-tournament-history.csv")

dplyr::glimpse(raw_df)
```

<br><br>

## Question 1

#### Is there a positive correlation between seed number and wins during regular season? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### Do 1st seeded teams have a higher average of tournament wins than 3rd seeded teams? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### Does stanford have more regular season wins than UCLA from 1982-2018? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### Does an at home first game equate to a higher amount of tournament games won overall? Your question should literally be a level-4 header.

### Methods
```{r read-examine-data}


```

### Answer

Replace this text with your answer to your question.
